Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-04-04 Archive/Measuring_the_price_of_anarchy_in_ccu_interactions.tex

\usepackage{graphicx,times}
\usepackage[toc,page]{appendix}
\usepackage{fullpage}
\usepackage[parfill]{parskip}
\usepackage{subfig}
\usepackage{caption}
\usepackage[figuresleft]{rotating}
\usepackage{float}
\usepackage{multibib}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{color}

@@

\title{Measuring the Price of Anarchy in Critical Care Unit Interactions}
\author{Vincent Knight*
    \and
        Izabela Komenda
    \and
        Jeff Griffiths}

@@

The main proposition of the work requested by the ABUHB was to develop a mathematical model of bed occupancies at the CCUs at RG and NH.
After an initial analysis of the data, behavioural aspects became apparent; for example, delaying patients discharge if there was no pressure on CCU beds, or admitting fewer patients if bed occupancy levels were high.
As a result of this, a state-dependent queueing model has been developed, which includes the dependency of admission rate on actual occupancy \cite{Komenda2013}.
This state dependent model was applied to both NH and RG separately.
It is however obvious that the actions of one CCU impact on the other CCU, as diversion of patients from one CCU to the other sometimes occurs.
A pictorial representation of the situation is given in Figure \ref{diagramofdiversion}.

@@

\begin{table}[!htbp]
\begin{center}
\begin{tabular}{c|lc}
\toprule
Parameter&Parameter description&Parameter value\\
\midrule
$c_{\NH}$&the bed capacity at NH&8\\
$c_{\RG}$&the bed capacity at RG&16\\
$\lambda_{\NH}$&the arrival rate at NH (per day)&1.50 \\
$\lambda_{\RG}$&the arrival rate at RG (per day)&2.24\\
$\mu_{\NH}$&the service rate at NH (days)&0.262\\
$\mu_{\RG}$&the service rate at RG (days)&0.198\\
$t$& bed utilisation target & 0.8\\
\bottomrule
\end{tabular}
\end{center}
\caption{Parameter values used in the model}\label{parameter_values_model_1}
\end{table}

@@

\begin{figure}[!htbp]
$$
\begin{array}{cc}
\includegraphics[width=.5\textwidth]{./Images/NH.pdf}&\includegraphics[width=.5\textwidth]{./Images/RG.pdf}\\
h=NH&h=RG
\end{array}
$$
\caption{Steady state probabilities for $h\in\{\NH,\RG\}$ with $(K_{\NH}, K_{\RG})=(6,12)$} \label{steady_state_probs}
\end{figure}

@@

\begin{figure}[!htbp]
$$
\begin{array}{cc}
\includegraphics[width=.5\textwidth]{./Images/NH_1_12.pdf}&\includegraphics[width=.5\textwidth]{./Images/RG_1_12.pdf}\\
h=\NH&h=\RG
\end{array}
$$
\caption{Steady state probabilities for $h\in\{\NH,\RG\}$ with $(K_{\NH}, K_{\RG})=(1,12)$} \label{steady_state_probs_1_12}
\end{figure}

@@

\begin{figure}[!htbp]
\hspace{2cm}For all $h\in\{\text{NH}, \text{RG}\}$ minimise:
$$\left(U_{h}-t\right)^2$$
\hspace{2cm}Subject to:
\begin{align}
0\leq & K_h \leq c_{h}\nonumber\\
&K_h \in  \mathbb{Z}\nonumber
\end{align}
\caption{The optimisation problem underlying the game}\label{model1}
\end{figure}

This game is equivalent to a bi matrix game with restriction to pure strategies where both players aim to get their utilisation as close as possible to a certain target.
As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, but based on discussions with ABUHB, long term threshold policies are a realistic consideration.

The following result is a sufficient condition for the existence of equilibrium:\\

@@

\begin{figure}[!htbp]
$$\begin{array}{cc}
\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_NH.pdf}&
\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_RG.pdf}
\end{array}$$
\caption{Plots of $f_{\NH}(K_{\RG})$ and $f_{\RG}(K_{\NH})$}\label{exampleforproof}
\end{figure}

@@

\begin{figure}[!hbtp]
\begin{center}
\includegraphics[width=.7\textwidth]{./Images/proof.pdf}
\end{center}
\caption{Graphical proof of the fact that $f_{\NH}(K_{\RG})<f_{\NH}(K_{\RG}+1)$}\label{proof}
\end{figure}

Let $k^*=f_{NH}(K_{\RG})$ for a given $K_{\RG}$.
As $K_{\RG}$ increases, the utilisation $U_{\NH}(k^*)$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
As $K_{RG}$ increases $\left(U_{NH}(k^*)-t\right)^2$ decreases until $U_{NH}(k^*)=t$ and then increases, however $\left(U_{NH}(k^*+1)-t\right)^2$ will continue to decrease.
Thus, $f_{\NH}(K_{\RG})\geq k^*$ as required.
\end{proof}

@@

The game theoretic model of Figure \ref{model1} is solved using exhaustive consideration of best responses whilst taking advantage of the structure identified by the Lemma of Section \ref{queueingandgamemodels}. For any given pair of threshold strategies the matrix equation $\pi Q=0$ is solved by obtaining a basis for the Kernel of $Q$. For the purpose of this paper this is implemented in \cite{sage}.

@@

For the parameters of Table \ref{parameter_values_model_1} the best responses are shown in Figure \ref{Fig:best_responses_model1}.
For example, in Figure \ref{Fig:best_responses_model1}a if RG chooses $K_{\RG}=6$, NH has best response $K_{\NH}=8$ .
Similarly, if $K_{\NH}=2$, RG has best response $K_{\RG}=15$.
A Nash equilibrium for our game is a pair of points that intersect.

\begin{figure}[!htbp]
$$
\begin{array}{cc}
\includegraphics[width=.5\textwidth]{./Images/best_responses_model1.pdf}&
\includegraphics[width=.5\textwidth]{./Images/best_responses_model1_t=0_6.pdf}\\
\text{(a: $t=0.8$)}&\text{(b: $t=0.6$)}
\end{array}
$$
\caption{Best responses for each hospital (a: $t=0.8$; b: $t=0.6$). The point of intersection is circled.} \label{Fig:best_responses_model1}
\end{figure}

For this model the Nash equilibrium is at $(8,16)$, which gives $\widetilde T=3.65$ and we obtain $T^*=3.65$.
Importantly, a PoA of 1 is not guaranteed for this problem.
For example in Figure \ref{Fig:best_responses_model1}b similar best response behaviour is shown for $t=0.6$ for which the $\text{PoA}=1.18$ (the optimal throughput is again at $(8,16)$).

Whilst removing central control, a certain influence can be exerted by a choice of $t$.
Figure \ref{Fig:target_demand_model1} (note: the non linear scale) and Table \ref{tabletargetdemandm1} show the effect of $t$ and overall demand.
We modify the demand rate from Table \ref{parameter_values_model_1} by taking $\lambda_h \leftarrow \lambda_h(1+x)$ for $-0.9\leq x\leq2$.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=.5\textwidth]{./Images/lnPoAmodel1targetvdemand.pdf}
\end{center}
\caption{PoA for different target and demand rates}\label{Fig:target_demand_model1}
\end{figure}

\begin{table}[!htbp]
\begin{center}
\begin{tabular}{c|ccccccccc}
\toprule
$x$&$t=0.15$&$t=0.27$&$t=0.4$&$t=0.52$&$t=0.64$&$t=0.76$&$t=0.88$&$t=1$\\
\midrule
-0.9&1.0&1.0&1.0&1.0&1.0&1.0&1.0&1.0\\
-0.61&1.64&1.04&1.0&1.0&1.0&1.0&1.0&1.0\\
-0.33&3.27&1.66&1.22&1.0&1.0&1.0&1.0&1.0\\
-0.03&4.43&2.55&1.64&1.34&1.06&1.0&1.0&1.0\\
0.26&5.23&2.99&2.1&1.51&1.28&1.09&1.0&1.0\\
0.55&7.34&3.21&2.25&1.74&1.34&1.16&1.0&1.0\\
0.84&7.6&3.81&2.32&1.79&1.46&1.17&1.03&1.0\\
1.13&7.73&3.88&2.36&1.82&1.48&1.25&1.04&1.0\\
1.41&7.81&3.91&2.61&1.97&1.58&1.26&1.09&1.0\\
1.7&7.86&3.94&2.63&1.98&1.58&1.32&1.14&1.0\\
1.99&7.89&3.95&2.64&1.98&1.59&1.33&1.14&1.0\\
\bottomrule
\end{tabular}
\end{center}
\caption{Numerical values of PoA for different target and demand rates}\label{tabletargetdemandm1}
\end{table}

We see that an extremely large PoA is obtained for $t<0.2$.
For values of $t>0.5$ the PoA is still high: a PoA of 2 corresponds to 100\% less throughput of patients.
These findings seem to give some backing to the targets implemented throughout the NHS \cite{Bevan2006}.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=10cm]{./Images/argminPoAmodel1.pdf}
\caption{Lowest value of $t$ ensuring PoA$=1$} \label{mintargetvdemand}
\end{center}
\end{figure}

@@

As before, Figure \ref{Fig:target_demand_model2} and Table \ref{tabletargetdemandm2} present the PoA for different target values and demand rate changes.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=10cm]{./Images/model2targetvdemand.pdf}
\caption{PoA for different target and demand rates for soft diversion} \label{Fig:target_demand_model2}
\end{center}
\end{figure}

\begin{table}[!htbp]
\begin{center}
\begin{tabular}{c|ccccccccc}
\toprule
$x$&$t=0.15$&$t=0.27$&$t=0.4$&$t=0.52$&$t=0.64$&$t=0.76$&$t=0.88$&$t=1$\\
\midrule
-0.9&1.0&1.0&1.0&1.0&1.0&1.0&1.0&1.0\\
-0.61&1.0&1.0&1.0&1.0&1.0&1.0&1.0&1.0\\
-0.32&1.01&1.01&1.01&1.01&1.0&1.0&1.0&1.0\\
-0.03&1.05&1.05&1.05&1.05&1.05&1.05&1.0&1.0\\
0.26&1.06&1.06&1.06&1.06&1.06&1.06&1.06&1.0\\
0.55&1.06&1.06&1.06&1.06&1.06&1.06&1.06&1.01\\
0.84&1.05&1.05&1.05&1.05&1.05&1.05&1.05&1.04\\
1.13&1.05&1.05&1.05&1.05&1.05&1.05&1.05&1.04\\
1.42&1.04&1.04&1.04&1.04&1.04&1.04&1.04&1.04\\
1.71&1.03&1.03&1.03&1.03&1.03&1.03&1.03&1.03\\
1.99&1.03&1.03&1.03&1.03&1.03&1.03&1.03&1.03\\
\bottomrule
\end{tabular}
\end{center}
\caption{Numerical values of PoA for different target and demand rates}\label{tabletargetdemandm2}
\end{table}

@@

Also, for very low values of demand, cooperation can be obtained with no target.
\begin{itemize}
    \item When the demand is low, there is no scope for uncoordinated behaviour to be damaging.
    \item When the demand is very high, the system is saturated and once again uncoordinated behaviour has no negative effect in comparison to optimal behaviour.
    \item There is however a region of demand for which there is a high PoA.
\end{itemize}

@@

 \begin{table}[!htbp]
\begin{center}
\begin{tabular}{ccccccc}
\toprule
%\textbf{Demand}&\textbf{Nash}&\multirow{2}{*}{\textbf{$\widetilde T$}}&\textbf{Nash NH}&\textbf{Nash RG}&\multirow{2}{*}{\textbf{$T^*$}}&\multirow{2}{*}{\textbf{PoA}}\\
%\textbf{change, $x$}&\textbf{equilibrium}&\textbf{ }&\textbf{throughput}&\textbf{throughput}&\textbf{}&\textbf{}\\
$x$&Nash Equilibrium&$\tilde T$&Nash $T_{NH}$& Nash $T_{RG}$& $T^*$& PoA\\
\midrule
0.1&(8,16)&3.92&1.50&2.42&3.92&1\\
0.2&(8,16)&3.92&1.50&2.42&3.92&1\\
0.3&(6,12)&4.19&1.65&2.54&4.33&1.03\\
0.4&(4,0)&4.22&1.65&2.57&4.48&1.06\\
0.5&(4,0)&4.22&1.65&2.57&4.48&1.06\\
0.6&(0,0)&4.42&1.69&2.72&4.68&1.06\\
\bottomrule
\end{tabular}
\end{center}
\caption{Soft diversion results for $t=0.8$}\label{table_model2_target_demand}
\end{table}

@@

Figure \ref{mintargetvdemandmodel2} shows the lowest values of $t$ which gives a PoA of 1.
We see that as demand increases this value also increases.
Also, for very low values of demand, cooperation can be obtained with no target.
For the actual demand ($x=0$) a target value of $t=0.72$ is once again recommended.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=12cm]{./Images/argminPoAmodel2.pdf}
\caption{Lowest value of $t$ ensuring PoA$=1$} \label{mintargetvdemandmodel2}
\end{center}
\end{figure}

@@

In this work a generic game theoretical model has been presented that accounts for the selfish actions of two CCUs.
This game theoretic model is underpinned by a queueing model that takes into account the stochastic nature of queueing systems.
This work extends the application of game theoretic models already present in the literature to healthcare \cite{li2002cooperative, xie2006note}.

A result is proved that allows for the assertion of existence of Nash equilibrium. This result is then applied to two particular models that are influenced by discussions with a local health board:

@@

\begin{figure}[!htbp]
$$\begin{array}{cc}
\includegraphics[width=.5\textwidth]{./Images/model1capacity.pdf}&
\includegraphics[width=.5\textwidth]{./Images/model2capacity.pdf}
\\
\text{a: Strict diversion}&\text{b: Soft diversion}\\
\end{array}$$
\caption{The effect of capacity on the PoA}\label{capacity}
\end{figure}

@@

\begin{itemize}
    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{naor1969regulation, shone2013comparisons});
    \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
    \item The restriction to pure strategies is influenced by discussions with ABUHB and also does not detract from the results presented thanks to the Theorem and Lemma of Section \ref{queueingandgamemodels}.  However, allowing for mixed strategies could also be of interest.
\end{itemize}

Despite these limitations the work presented here gives a strong analytical evidence as to the use of policies in a decentralised healthcare environmenta local health board could involve the investigation of patient survival instead of throughput as utility.
This would be similar to work such as \cite{erkut2008ambulance, knight2012ambulance}.

The code used in this work can be found here: \url{https://github.com/drvinceknight/Measuring_the_price_of_anarchy_in_ccu_interactions}.
The graphics for this paper were obtained using \cite{Hunter:2007, sage} a worksheet with the data and code used for the plots can be found here: \url{https://sage.maths.cf.ac.uk/home/pub/122/}.

>>>>

\usepackage{graphicx,times}
\usepackage[toc,page]{appendix}
\usepackage{fullpage}
\usepackage[parfill]{parskip}
\usepackage{subfig}
\usepackage{caption}
\usepackage[figuresleft]{rotating}
\usepackage{float}
\usepackage{multibib}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{color}

@@

\title{Measuring the Price of Anarchy in Critical Care Unit Interactions}
\author{Izabela Komenda*
    \and
        Jeff Griffiths
    \and
        Vincent Knight}

@@

The main proposition of the work requested by the ABHB was to develop a mathematical model of bed occupancies at the CCUs at RG and NH.
After an initial analysis of the data, behavioural aspects became apparent; for example, delaying patients discharge if there was no pressure on CCU beds, or admitting fewer patients if bed occupancy levels were high.
As a result of this, a state-dependent queueing model has been developed, which includes the dependency of admission rate on actual occupancy \cite{Komenda2013}.
This state dependent model was applied to both NH and RG separately.
It is however obvious that the actions of one CCU impact on the other CCU, as diversion of patients from one CCU to the other sometimes occurs.
A pictorial representation of the situation is given in Figure \ref{diagramofdiversion}.

@@

\begin{table}[!htbp]
\begin{center}
\begin{tabular}{|c|l|c|}
\hline
\textbf{Parameter}&\textbf{Parameter description}&\textbf{Parameter value}\\
\hline
$c_{\NH}$&the bed capacity at NH&8\\
\hline
$c_{\RG}$&the bed capacity at RG&16\\
\hline
$\lambda_{\NH}$&the arrival rate at NH (per day)&1.50 \\
\hline
$\lambda_{\RG}$&the arrival rate at RG (per day)&2.24\\
\hline
$\mu_{\NH}$&the service rate at NH (days)&0.262\\
\hline
$\mu_{\RG}$&the service rate at RG (days)&0.198\\
\hline
$t$& bed utilisation target & 0.8\\
\hline
\end{tabular}
\end{center}
\caption{Parameter values used in the model}\label{parameter_values_model_1}
\end{table}

@@

\begin{figure}[!htbp]
$$
\begin{array}{cc}
\includegraphics[width=.5\textwidth]{NH.pdf}&\includegraphics[width=.5\textwidth]{RG.pdf}\\
h=NH&h=RG
\end{array}
$$
\caption{Steady state probabilities for $h\in\{\NH,\RG\}$ with $(K_{\NH}, K_{\RG})=(6,12)$} \label{steady_state_probs}
\end{figure}

@@

\begin{figure}[!htbp]
$$
\begin{array}{cc}
\includegraphics[width=.5\textwidth]{NH_1_12.pdf}&\includegraphics[width=.5\textwidth]{RG_1_12.pdf}\\
h=\NH&h=\RG
\end{array}
$$
\caption{Steady state probabilities for $h\in\{\NH,\RG\}$ with $(K_{\NH}, K_{\RG})=(1,12)$} \label{steady_state_probs_1_12}
\end{figure}

@@

\begin{figure}[!htbp]
\hspace{2cm}For all $h\in\{\text{NH}, \text{RG}\}$ maximize:
$$U_{h}$$
\hspace{2cm}Subject to:
\begin{align}
0\leq & K_h \leq c_{h}\nonumber\\
&K_h \in  \mathbb{Z}\nonumber\\
&U_h\leq t\nonumber
\end{align}
\caption{The optimisation problem underlying the game}\label{model1}
\end{figure}

\todoVK{We have a problem here, how do we know that a solution always exists? Might need to change problem to not have target as a contraint but instead simply consider distance from constraint. The problem with that is that we won't necessarily have the existence theorem anymore... I need to figure this out.}
This game is equivalent to a bi matrix game with restriction to pure strategies where both players aim to get their utilisation as close to, without going past, a certain target.
As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, but based on discussions with ABHB, long term threshold policies are a realistic consideration.

The following result is a sufficient condition for the existence of equilibria:\\

@@

\begin{figure}[!htbp]
$$\begin{array}{cc}
\includegraphics[width=.5\textwidth]{best_responses_ex_for_proof_NH.pdf}&
\includegraphics[width=.5\textwidth]{best_responses_ex_for_proof_RG.pdf}
\end{array}$$
\caption{Plots of $f_{\NH}(K_{\RG})$ and $f_{\RG}(K_{\NH})$}\label{exampleforproof}
\end{figure}

@@

\begin{figure}[!hbtp]
\begin{center}
\includegraphics[width=.7\textwidth]{proof.pdf}
\end{center}
\caption{Graphical proof of the fact that $f_{\NH}(K_{\RG})<f_{\NH}(K_{\RG}+1)$}\label{proof}
\end{figure}

Let $k^*=f(K_{\RG})$ for a given $K_{\RG}$.
As $K_{\RG}$ increases, the utilisation $U_{\NH}$ for $k^*$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
Thus, $f_{\NH}(K_{\RG})\geq k^*$: strict inequality depending on whether or not the utilisation for $K_{\NH}>k^*$ is below $t$.
\end{proof}

@@

@@

For the parameters of Table \ref{parameter_values_model_1} the best responses are shown in Figure \ref{Fig:best_responses_model1}.
For example, in Figure \ref{Fig:best_responses_model1}a if RG chooses $K_{\RG}=6$, NH has best response $K_{\NH}=7$ .
Similarly, if NH has best response $K_{\NH}=3$, RG has best response $K_{\RG}=15$.
A Nash equilibrium for our game is a pair of points that intersect (in this case: $(K_{\NH}, K_{\RG})=(8,16)$ is a Nash equilibrium).

\begin{figure}[!htbp]
$$
\begin{array}{cc}
\includegraphics[width=.5\textwidth]{best_responses_model1.pdf}&
\includegraphics[width=.5\textwidth]{best_responses_model1_t=0_6.pdf}\\
\text{(a: $t=0.8$)}&\text{(b: $t=0.6$)}
\end{array}
$$
\caption{Best responses for each hospital (a: $t=0.8$; b: $t=0.6$). The point of intersection is circled.} \label{Fig:best_responses_model1}
\end{figure}

For this model the Nash equilibrium is at $(8,16)$, which gives $\widetilde T=3.64$ and we obtain $T^*=3.64$.
Importantly, a PoA of 1 is not guaranteed for this problem.
For example in Figure \ref{Fig:best_responses_model1}b similar best response behaviour is shown for $t=0.6$ for which the PoA$=1.18$ (the optimal throughput is again at $(8,16)$).

Whilst removing central control, a certain influence can be exerted by a choice of $t$.
Figure \ref{Fig:target_demand_model1} shows the effect of $t$ and overall demand. Note, the non linear scale in \ref{Fig:target_demand_model1}a.
We modify the demand rate from Table \ref{parameter_values_model_1} by taking $\lambda_h \leftarrow \lambda_h(1+x)$ for $-0.9\leq x\leq2$.

\begin{figure}[!htbp]
$$
\begin{array}{cc}
\includegraphics[width=.5\textwidth]{lnPoAmodel1targetvdemand.pdf}
&
\includegraphics[width=.5\textwidth]{model1targetvdemandfort-5.pdf}\\
\text{(a)}&\text{(b)}
\end{array}
$$
\caption{PoA for different target and demand rates (the second plot is a given region of the first)} \label{Fig:target_demand_model1}
\end{figure}

We see that an extremely large PoA is obtained for $t<0.2$. If we concentrate on a value of $t>0.5$ then the PoA is still extremely high: a PoA of 1.9 corresponds to 90\% less throughput of patients.
These findings seem to give some backing to the targets implemented throughout the NHS \cite{Bevan2006}.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=10cm]{argminPoAmodel1.pdf}
\caption{Lowest value of $t$ ensuring PoA$=1$} \label{mintargetvdemand}
\end{center}
\end{figure}

@@

As before, Figure \ref{Fig:target_demand_model2} presents the PoA for different target values and demand rate changes.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=10cm]{model2targetvdemand.pdf}
\caption{PoA for different target and demand rates for soft diversion} \label{Fig:target_demand_model2}
\end{center}
\end{figure}

@@

\begin{itemize}
    \item When the demand is low, there is no scope for uncoordinated behaviour to be damaging.
    \item When the demand is very high, the system is saturated and once again uncoordinated behaviour has no negative effect in comparison to optimal behaviour.
    \item There is however a region of demand for which there is a high PoA.
\end{itemize}

@@

 \begin{table}[!htbp]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Demand}&\textbf{Nash}&\multirow{2}{*}{\textbf{$\widetilde T$}}&\textbf{Nash NH}&\textbf{Nash RG}&\multirow{2}{*}{\textbf{$T^*$}}&\multirow{2}{*}{\textbf{PoA}}\\
\textbf{change, $x$}&\textbf{equilibrium}&\textbf{ }&\textbf{throughput}&\textbf{throughput}&\textbf{}&\textbf{}\\
\hline
0.1&(8,16)&3.91&1.51&2.41&3.91&1\\
0.2&(8,15)&4.11&1.63&2.48&4.14&1.06\\
0.3&(5,10)&4.11&1.63&2.48&4.31&1.07\\
0.4&(4,0)&4.20&1.65&2.55&4.46&1.06\\
0.5&(3,0)&4.30&1.66&2.64&4.57&1.06\\
0.6&(0,0)&4.39&1.68&2.71&4.65&1.06\\
\hline
\end{tabular}
\end{center}
\caption{Soft diversion results for $t=0.8$}\label{table_model2_target_demand}
\end{table}

@@

Figure \ref{mintargetvdemandmodel2} shows the lowest values of $t$ which gives a PoA of 1.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=12cm]{argminPoAmodel2.pdf}
\caption{Lowest value of $t$ ensuring PoA$=1$} \label{mintargetvdemandmodel2}
\end{center}
\end{figure}

@@

In this work a generic game theoretical model has been presented that accounts for selfish actions of two CCUs.
This game theoretic model is underpinned by a queueing model that takes into account the stochastic nature of queueing systems.
This work extends the application of Game Theoretic models already present in the literature to healthcare \cite{li2002cooperative, xie2006note}.

A result is proved that allows for the assertion of existence of Nash equilibrium. This result is then applied to two particular models that are influenced by discussions with ABHB:

@@

\begin{figure}[!htbp]
$$\begin{array}{cc}
\includegraphics[width=.5\textwidth]{model1capacity.pdf}&
\includegraphics[width=.5\textwidth]{model2capacity.pdf}
\\
\text{a: Strict diversion}&\text{a: Soft diversion}\\
\end{array}$$
\caption{The effect of capacity on the PoA}\label{capacity}
\end{figure}

@@

\begin{itemize}
    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{knight2012comparisons, naor1969regulation});
    \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
    \item The restriction to pure strategies is influenced by discussions with ABHB and also does not detract from the results presented thanks to the Theorem and Lemma of Section \ref{queueingandgamemodels}.  However, allowing for mixed strategies could also be of interest.
\end{itemize}

Despite these limitations the work presented here gives a strong analytical evidence as to the use of policies in a decentralised healthcare environment.

Further work could involve the investigation of patient survival instead of throughput as utility.
This would be similar to work such as \cite{erkut2008ambulance, knight2012ambulance}.

The code used in this work was written in Python and can be found here: \url{drvinceknight/measuring...}.
The graphics for this paper were obtained using \cite{Hunter:2007, sage} a worksheet with the data and code used for the plots can be found here: \url{https://sage.maths.cf.ac.uk/home/pub/120/}.
